Fusing Filters with Integer Linear Programming

### 2014-05-15 2014betterfusionforfilters/section/04-ILP.tex
More on linear constraints

\paragraph{Acyclic and precedence-preserving} The first group of constraints ensures that the clustering is acyclic:
\begin{tabbing}
MM  \= MMM \= M \= MMM \= M \= MMMM \= \kill
    \>    $x_{ij}$ \> $\le$ \> $\pi_j - \pi_i$ \> $\le$ \> $N x_{ij}$ 
    \>             (with an edge from $i$ to $j$)            \\
    \> $-N x_{ij}$ \> $\le$ \> $\pi_j - \pi_i$ \> $\le$ \> $N x_{ij}$ 
    \>             (with no edge from $i$ to $j$)
\end{tabbing}
As per Megiddo~\cite{megiddo1998optimal} the form of these constraints is determined by whether there is an dependency between nodes $i$ and $j$. The $N$ value is set to the total number of nodes in the graph.

@@

\paragraph{Fusion-preventing edges}
\begin{tabbing}
MMMMM   \= MMM \= M \= MMM \= M \= MMM \= \kill
Minimise   \> \ldots \\
Subject to \> \ldots \\
           \> $x_{ij}$    \> $=$   \> $1$             \>       \>            \\
           \> (fusion-preventing edges from $i$ to $j$)      \\
           \> \ldots
\end{tabbing}
As per Megiddo\cite{megiddo1998optimal}, for every fusion-preventing edge, we add the constraint $x_{ij} = 1$, so that no fusion can occur. This, together with the precedence constraints above, has the effect of enforcing $\pi_i < \pi_j$.

\paragraph{Fusion between different iteration sizes}

>>>>

% -------------------------------------
\paragraph{Acyclic and precedence-preserving} The first group of constraints ensures that the clustering is acyclic:
\begin{tabbing}
MM  \= MMM \= M \= MMM \= M \= MMMM \= \kill
    \>    $x_{ij}$ \> $\le$ \> $\pi_j - \pi_i$ \> $\le$ \> $N x_{ij}$ 
    \>             (with an edge from $i$ to $j$)            \\
    \> $-N x_{ij}$ \> $\le$ \> $\pi_j - \pi_i$ \> $\le$ \> $N x_{ij}$ 
    \>             (with no edge from $i$ to $j$)
\end{tabbing}
As per Megiddo~\cite{megiddo1998optimal} the form of these constraints is determined by whether there is an dependency between nodes $i$ and $j$. The $N$ value is set to the total number of nodes in the graph.

@@

% -------------------------------------
\paragraph{Fusion-preventing edges} As per Megiddo\cite{megiddo1998optimal}, if there is a fusion preventing edge between two nodes we add a constraint to ensure the nodes will be placed in different clusters.
\begin{tabbing}
MMMMM   \= MMM \= M \= MMM \= M \= MMM \= \kill
           \> $x_{ij}$    \> $=$   \> $1$ \>       \>       \\
           \> (for fusion-preventing edges from $i$ to $j$) 
\end{tabbing}
When combined with the precedence-preserving constraints earlier, setting $x_{ij} = 1$ also forces $\pi_i < \pi_j$.

% -------------------------------------
\paragraph{Fusion between different iteration sizes}
